### 2016-09-26 notions.tex
making a pass through the results section, especially the lin, bi-lin, ds constructions
notes

We formalize two types of privacy notions. The first captures
a ``one-wayness'' property that (informally) requires that
the public representation of a set~$S$ does not make it any easier for an attacker
to learn elements of~$S$.
The second definition
captures a flavor of semantic security, essentially requiring that $\pub$ does
not leak any information about the set~$S$ it represents beyond
what is captured by some explicit leakage function.

Our one-wayness notion is defined in Figure~\ref{fig:privacy-ow}.
The relevant experiment begins by first sampling a set $S$ according to a distribution
${\cal D}$. Then $\Rep(S)$ is run to obtain $\pubaux,\privaux$, and the attacker~$A$ is given
$\pubaux$. The attacker succeeds if it is able to output an element of~$S$.
We define the advantage of adversary~$A$ in this experiment\footnote{We
remark that one could consider augmenting experiment $\ExpPrivOW{\Pi,{\cal D}}{A}$ by additionally
giving $A$ access to an oracle for testing membership in~$S$. However, it is not hard
to see that allowing $q$ such queries can increase $A$'s advantage by at most a factor of~$q$.} as
$\AdvPrivOW{\Pi,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\Pi,{\cal D}}{A}=1}$ and,
overloading notation, we write $\AdvPrivOW{\Pi,{\cal D}}{t}$ for the maximum of this value over
all~$t$-time adversaries.
Noting that an attacker can trivially succeed with probability
$2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$,
we say a
set-representation data structure~$\Pi$ is $(t,\epsilon)$-ow-private if for all ${\cal D}$
we have $\AdvPrivOW{\Pi,{\cal D}}{t} - 2^{-H_\infty({\cal D})} \leq \epsilon$.
\jnote{Not sure I'm completely happy with the definition.}

@@

Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
\jnote{Here it would not be hard to write the definition for general data structures, not
specifically set-multiplicity data structures.}
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
%\footnote{We do not give $A$ an oracle for issuing queries;
%since $A$ knows the set~$S$, such an oracle would be superfluous.
%\jnote{Interestingly,
%if we provided a query oracle in the real world and an oracle that returns the correct
%answer in the simulated world, then the definition seems to imply
%correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
if for all efficient $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small. \jnote{Do we want to
write a formal $t, \epsilon$-style definition?}
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{The definition
as stated does not really work well in the presence of (programmable) random oracles.}
\jnote{In the current definition there is (intentionally) no bound on the simulator's
running time.}

@@

%
%\begin{figure}[htbp]
%\centering
%\hfpages{.495}
%{
%\hpagess{.49}{.49}
%{
%
%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
%$S\getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr A^{\TestOracle}(M,\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
%
%\medskip
%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
%$S\getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr P(\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
%}
%%
%{
%\oracle{$\TestOracle(q)$}\\
%$a \gets \Qry(M,\pubaux,\privaux,q)$\\
%Return~$a$\\
%}
%}
%{
%\hpagess{.49}{.49}
%{
%\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
%$S\getsr \distr{}{}$\\
%$b \getsr \bits$\\
%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
%$M_0 \getsr P(\pubaux)$\\
%%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
%$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
%%if $f(S)=v$ then\\
%if $b'=b$ then\\
%\nudge Return 1\\
%Return 0\\
%%
%%\medskip
%%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
%%$S\getsr \distr{}{}$\\
%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%%$(f,v) \getsr P(\pubaux)$\\
%%if $f(S)=v$ then\\
%%\nudge Return 1\\
%%Return 0\\
%}
%%
%{
%\oracle{$\TestOracle(q)$}\\
%$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
%Return~$a$\\
%}
%}
%\caption{Semantic-security style privacy
%  definitions. \textcolor{red}{On the left, need to protect against
%    adversary outputting
%    things like $f(S)=M$.  One idea is to forbid~$f$ such that
%    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
%    }
%\label{fig:privacy-ss}
%\end{figure}

@@

>>>>

\tsnote{I think we should switch the order of presentation, since we
  use the SS notion much more. }
We formalize two types of privacy notions. The first captures
a ``one-wayness'' property that (informally) requires that
the public representation of a set~$S$ does not make it any easier for an attacker
to learn elements of~$S$.  The second definition
captures a flavor of semantic security, essentially requiring that $\pub$ does
not leak any information about the set~$S$ it represents beyond
what is captured by some explicit leakage function.

Our one-wayness notion is defined in Figure~\ref{fig:privacy-ow}.
The relevant experiment begins by first sampling a set $S$ according to a distribution
${\cal D}$. Then $\Rep(S)$ is run to obtain $\pubaux,\privaux$, and the attacker~$A$ is given
$\pubaux$. The attacker succeeds if it is able to output an element of~$S$.
We define the advantage of adversary~$A$ in this experiment\footnote{We
remark that one could consider augmenting experiment $\ExpPrivOW{\Pi,{\cal D}}{A}$ by additionally
giving $A$ access to an oracle for testing membership in~$S$. However, it is not hard
to see that allowing $q$ such queries can increase $A$'s advantage by at most a factor of~$q$.} as
$\AdvPrivOW{\Pi,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\Pi,{\cal D}}{A}=1}$ and,
overloading notation, we write $\AdvPrivOW{\Pi,{\cal D}}{t}$ for the maximum of this value over
all~$t$-time adversaries.
We remark that an attacker can trivially achieve advantage
$2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$.

@@

Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
\jnote{Here it would not be hard to write the definition for general data structures, not
specifically set-multiplicity data structures.}
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
%\footnote{We do not give $A$ an oracle for issuing queries;
%since $A$ knows the set~$S$, such an oracle would be superfluous.
%\jnote{Interestingly,
%if we provided a query oracle in the real world and an oracle that returns the correct
%answer in the simulated world, then the definition seems to imply
%correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
if for all efficient $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{The definition
as stated does not really work well in the presence of (programmable) random oracles.}
\jnote{In the current definition there is (intentionally) no bound on the simulator's
running time.}

@@

@@

\jnote{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}
